An exact Riemann solver for multi-material elastic-plastic flows with Mie-Gr\"uneisen equation of state

### 2019-05-31 TikzFig/Tikz.tex
third
2
11111

\begin{tikzpicture}[node distance=2cm]
%定义流程图具体形状
\node (start1) [startstop] {$\rho_L^*$};
\node (start2) [startstop,right of=start1, xshift = 1cm] {$\rho_R^*$};
\node (pro1) [process, below of=start1, yshift=0.2cm, left of=start1, xshift=0.8cm] {$p_L^*,s_{xxL}^*,u_L^*$};
\node (pro2) [process, right of=pro1, xshift= 3.7cm] {$p_R^*,s_{xxR}^*,u_R^*$};
\node (dec1) [decision, below of=pro1, yshift= -0.5cm, xshift=3.0cm] {Convergence ?};
\node (stop) [startstop, below of=dec1] {Output with $\mathbf{Q}_L^*$ and $\mathbf{Q}_R^*$};

%连接具体形状
\draw [arrow](start1) -- (pro1);
\draw [arrow](start2) -- (pro2);
\draw [arrow](pro1) -- (dec1);
\draw [arrow](pro2) -- (dec1);
\draw [arrow](dec1) -- ($(dec1.east) + (2.5,0)$) node[anchor=north] {NO}  |- node [anchor =south] {A new $\rho_R^*$} (start2);
\draw [arrow](dec1) -- ($(dec1.west) + (-2.8,0)$) node[anchor=north] {NO} |- node [anchor =south] {A new $\rho_L^*$}(start1);
%\draw [arrow](dec1) -- ($(dec1.east) + (1.5,0)$) node[anchor=north] {NO} |- (pro2);
\draw [arrow](dec1) -- node[anchor=west] {YES} (stop);
\end{tikzpicture}

>>>>

\begin{tikzpicture}[node distance=2cm]
%定义流程图具体形状
  \node (start1) [startstop] {$\rho_L^*$};
\node (start2) [startstop,right of=start1,xshift=2cm] {$\rho_R^*$};
\node (decL) [decision, below of=start1,xshift=-0.1cm] {\tiny Left case determined};
\node (decR) [decision, below of =start2,xshift=0.1cm] {\tiny  Right case determined};
\node (pro1) [process, below of=decL] {$p_L^*,s_{xxL}^*,u_L^*$};
\node (pro2) [process, below of = decR]{$p_R^*,s_{xxR}^*,u_R^*$};
\node (dec1) [decision, below of=pro1,xshift = 2.5cm] {Convergence ?};
\node (stop) [startstop, below of=dec1] {Output with $\mathbf{Q}_L^*$ and $\mathbf{Q}_R^*$};

%连接具体形状
\draw [arrow](start1) -- (decL);
\draw [arrow](decL) -- (pro1);
\draw [arrow](decR) -- (pro2);
\draw [arrow](start2) -- (decR);
\draw [arrow](pro1) -- (dec1);
\draw [arrow](pro2) -- (dec1);
\draw [arrow](dec1) -- ($(dec1.east) + (1.8,0)$) node[anchor=north] {NO}  |- node [anchor =south] {A new $\rho_R^*$} (start2);
\draw [arrow](dec1) -- ($(dec1.west) + (-2.5,0)$) node[anchor=north] {NO} |- node [anchor =south] {A new $\rho_L^*$}(start1);
%\draw [arrow](dec1) -- ($(dec1.east) + (1.5,0)$) node[anchor=north] {NO} |- (pro2);
\draw [arrow](dec1) -- node[anchor=west] {YES} (stop);
\end{tikzpicture}

  \begin{tikzpicture}
    \draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (4,0) node[below]{$x$};
    \draw [line width =1pt] (-4,0) -- (0,0);
    \draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (0,4) node[left]{$t$};
    \draw [double](0,0) -- ([turn]165:3.5)   node [above]{Contact};
	\draw  (0,0) node[below]{$O$} -- ([turn]135:3.5) node [above]{Right elastic};
    \draw  (0,0) -- ([turn]-135:3.5) node [above]{Left elastic} ;
    \node at (-1.3,0.5) {$\mathbf{Q}_L$};
    \node at (-0.6,1.2) {$\mathbf{Q}_L^*$};
    \node at (0.7,1.2) {$\mathbf{Q}_R^*$};
    \node at (1.3,0.5) {$\mathbf{Q}_R$};
\end{tikzpicture}

% Half Riemann solver

  \begin{tikzpicture}
	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (4,0) node[below]{$x$};
	\draw [line width =1pt] (-4,0) -- (0,0);
	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (0,4) node[left]{$t$};
%	\draw [double](0,0)  -- ([turn]165:3.5)   node [above]{Contact};

	\draw  (0,0) -- ([turn]152:3.5);
	\draw  (0,0) [line width = 0.8pt] node [below]{ $O$ }  -- ([turn]155:3.5) node [above]{Right wave};
	\node at (-1.7,1.2) {$\mathbf{Q}*$};
	\node at (-1.7,2.2) {With a fixed $u^*$ or $\sigma^*$};
	\node at (1.7,1.2) {$\mathbf{Q}_R$};
\end{tikzpicture}

  \begin{tikzpicture}
	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (4,0) node[below]{$x$};
	\draw [line width =1pt] (-4,0) -- (0,0);
	\draw [line width =1pt,-{Stealth[length=2.5mm]}] (0,0) -- (0,4) node[left]{$t$};
%	\draw [double](0,0)  -- ([turn]165:3.5)   node [above]{Contact};

	\draw  (0,0) [line width = 0.8pt] node [below]{ $O$ }  -- ([turn]155:3.5) node [above]{Elastic shock};
	\node at (-1.7,1.2) {$\mathbf{Q}*$};
	\node at (-1.7,2.2) {With a fixed $u^*$ or $\sigma^*$};
	\node at (1.7,1.2) {$\mathbf{Q}_R$};
\end{tikzpicture}
